---
title: "Trending Videso (Stats)"
output: html_document
---
---
title: "Youtube Stats"
author: "Jasmine Brown"
date: "8/8/2019"
output: html_document
---


Statistical Analysis

Now that the data set is cleaned, it is time for the statistical analysis. This analysis is the exploratory portion of the project. At this time, we are trying to find trends in the project data based on the facts and develop a solid hypothesis. In this portion of the coding in R, plots are created and analyzed. A deep analysis of the trending videos is investigated.


The necessary libraries needed for the project has been installed and are loaded here.

```{r}

library(tidyverse) #The swiss knife!

library(ggplot2)

library(rmarkdown)

library(caret)
```

All of the packages are loaded.  Therefore, we load the data into R and call the data frame dta.

```{r}

df_1clean <- read.csv("df_1clean.csv")

```



When reading in the data file, an additional variable appears.  That variable is removed.  A glimpse of the data set is called to determine the type of variables and ensure that the data set is correct.
```{r}

df_1clean <- select(df_1clean, -c(X))
glimpse(df_1clean)

```


The table shows that there is 7 variables and 29,943 observations.  The variables are labelled as factor and integer.  

Since there is an enormous amount of data for trending videos, the means of each variable is explored.  The code to find the means is written below.



```{r}

daily_means <- df_1clean  %>%
  group_by(trending_date) %>%
  summarise(n_title = n(),
            mean_likes = mean(likes),
             mean_views = mean(views),
             mean_dislikes = mean(dislikes),
            mean_comment_count = mean(comment_count))
daily_means

```

The mean for the variables, likes, dislikes, views, and comment_count is collect for each trending date.  The table also shows the number of videos per date.  A graphical analysis of the means is annotated in the code below.  We conduct this anlysis as it reduces the number of data points and patterns can be seen.  


```{r}

ggplot(daily_means, aes(y = mean_views, x = mean_likes, color=mean_dislikes)) + geom_point() + geom_jitter()

ggplot(daily_means, aes(y = mean_views, x = mean_likes, color=(mean_comment_count))) + geom_point() + geom_jitter()

ggplot(daily_means, aes(y = mean_views, x = mean_comment_count,  color=mean_dislikes)) + geom_point() + geom_jitter()

ggplot(daily_means, aes(y = mean_views, x = mean_dislikes,color=mean_comment_count)) + geom_point() + geom_jitter()

```
The plots show strong positive relationships between the means of the independent and dependent variables.  Thus there may be a strong correlation between the actual variables.  Note that a trending video that has an extremely large number of likes and views it also has a vast amount of dislikes and comments.  








```{r}
bp <- ggplot(df_1clean, aes(x=Popularity_Index, y=likes, fill=Popularity_Index)) + 
  geom_boxplot()+
  labs(title="Plot of Views Given Likes",x="Popularity Index", y = "Number of Views")+
scale_x_discrete(limits=c("Popular", "Highly Popular"))
bp + theme_classic()
```

There are too many outliers to use a box plot :( .  I leave it to show the complete anlysis that was conducted.



Let's take a look at the Popularity_Index variable that was created.
```{r}
df_1clean$Popularity_Index <- ifelse(df_1clean$Popularity_Index == 1, 'Highly Popular', 'Popular')
ggplot(df_1clean, aes(x = likes, y = views, color=Popularity_Index)) +
  geom_point() + geom_jitter()

ggplot(df_1clean, aes(x = dislikes, y = views, color=Popularity_Index)) +
  geom_point() + geom_jitter()

ggplot(df_1clean, aes(x = comment_count, y = views, color=Popularity_Index)) +
  geom_point() + geom_jitter()
```

Recall that the variables Popularity _Index was determined by the mean of views in the original data set.  It seems as if the clean data set includes the majority of highly popular videos.  Looking at the plots there are only a few popular trending videos as indicated by the small splash of mint green.


```{r}
 hist_plot <-
   df_1clean %>%
     ggplot(aes(x = views)) +
     geom_histogram(color = "maroon", fill = "dodgerblue", bins = 205)
  print(hist_plot)
  
  hist_plot <-
   df_1clean %>%
     ggplot(aes(x = likes)) +
     geom_histogram(color = "maroon", fill = "dodgerblue", bins = 205)
  print(hist_plot)
  
  hist_plot <-
   df_1clean %>%
     ggplot(aes(x = dislikes)) +
     geom_histogram(color = "maroon", fill = "dodgerblue", bins = 205)
  print(hist_plot)
  
  hist_plot <-
   df_1clean %>%
     ggplot(aes(x = comment_count)) +
     geom_histogram(color = "maroon", fill = "dodgerblue", bins = 205)
  print(hist_plot)
  
  
```
In the histograms, 205 bins were used because there were 205 dates.  The histograms generally have the same shape. The number of dislikes is fewer than any other variable. The variable views have a more extensive amount spread. Additonal histrograms are shown below.




```{r}
write.csv(daily_means, file = "daily_means.csv")
```





